\documentclass[a4paper, parskip=full]{memoir}
\setulmarginsandblock{2.5cm}{3cm}{*} % Upper-Lower margins
\setlrmarginsandblock{3.8cm}{2.5cm}{*} % Left-Right margins
\checkandfixthelayout

\usepackage{xspace}
\usepackage{times}
\usepackage{parskip}
\setlength{\parindent}{1.2cm} % Paragraph indent
\frenchspacing % Use single space after end of sentence

\input{../iiumthesis-config}

\begin{document}
\thispagestyle{empty}

\begin{LARGE}
\begin{center}
\MakeUppercase{Acknowledgments}\\[24pt]
\end{center}
\end{LARGE}

\noindent All glory is due to Allah, the Almighty, whose Grace and Mercy have 
been with me throughout the duration of my program.\\

I am most indebted to by supervisor, Assoc. Prof. Dr Name, whose enduring
disposition, kindness, promptitude, thoroughness and friendship have 
facilitated the successful completion of my work. I put on record and 
appreciate his detailed comments, useful suggestions and inspiring queries 
which have considerably improved this thesis. His brilliant grasp of the aim 
and content of this work led to his insightful comments, suggestions and 
queries which helped me a great deal. Despite his commitments, he took time to 
listen and attend to me whenever requested. The moral support he extended to me 
is in no doubt a boost that helped in building and writing the draft of this 
research work. I am also grateful to my co-supervisor, Asst. Prof. Dr. Name, 
whose support and cooperation contributed to the outcome of this work.\\

Lastly, my gratitude goes to my beloved wife and lovely children; for their
prayers, understanding and endurance while away.\\

Once again, we glorify Allah for His endless mercy on us one of which is
enabling us to successfully round off the efforts of writing this thesis. 
Al\d{h}amdulillah.\\
\end{document}